TO CHANGE: Web Service Community \\ Learning

### 2014-07-09 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Web Service Community \\ Learning}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} to other web services is. It is the difference between web service's \emph{response time} metric and the maximum value of response time of web services, that the web service has recently gathered information about.
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks compared to other competing web services. It is the difference between web service's \emph{throughput} metric and the maximum value of throughput of web services, that the web service has recently gathered information about.
\end{itemize}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{TO CHANGE: Web Service Community \\ Learning}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} to other web services is. It is the difference between web service's \emph{response time} metric and the maximum value of response time of web services, that the web service has recently gathered information about.
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services. It is the difference between web service's \emph{throughput} metric and the maximum value of throughput of web services, that the web service has recently gathered information about.
\end{itemize}
